---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```




```{r, include=FALSE}

options("width"=110)
options(max.print=100)

tmp <- packageDescription( basename(getwd()) )

```


```{r, results='asis', echo=FALSE}
cat("##", tmp$Title)
```



```{r, include=FALSE}
filelist.R   <- list.files("R", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.tests   <- list.files("tests", recursive = TRUE, pattern="\\.R$", ignore.case = TRUE, full.names = TRUE)
filelist.cpp <- list.files("src", recursive = TRUE, pattern="\\.cpp$", ignore.case = TRUE, full.names = TRUE)
lines.R      <- unlist(lapply(filelist.R, readLines))
lines.tests  <- unlist(lapply(filelist.tests, readLines))
lines.cpp    <- unlist(lapply(filelist.cpp, readLines))
length.R     <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.R,  value = TRUE, invert = TRUE))
length.tests <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.tests,  value = TRUE, invert = TRUE))
length.cpp   <- length(grep("(^\\s*$)|(^\\s*#)|(^\\s*//)", lines.cpp,  value = TRUE, invert = TRUE))
```






**Status**


*lines of R code:* `r length.R`, *lines of test code:* `r length.tests`

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<a href="https://travis-ci.org/petermeissner/sar"><img src="https://api.travis-ci.org/petermeissner/sar.svg?branch=master"><a/>
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/petermeissner/sar?branch=master&svg=true)](https://ci.appveyor.com/project/petermeissner/sar)
<a href="https://codecov.io/gh/petermeissner/sar"><img src="https://codecov.io/gh/petermeissner/sar/branch/master/graph/badge.svg" alt="Codecov" /></a>
<!--<a href="https://cran.r-project.org/package=sar"><img src="http://www.r-pkg.org/badges/version/sar"></a>
[![cran checks](https://cranchecks.info/badges/summary/reshape)](https://cran.r-project.org/web/checks/check_results_reshape.html)
<img src="http://cranlogs.r-pkg.org/badges/grand-total/sar">
<img src="http://cranlogs.r-pkg.org/badges/sar">
-->




**Development version**

```{r, include=FALSE}
source_files <- 
  grep(
    "/R/|/src/|/tests/",
    list.files(recursive = TRUE, full.names = TRUE), 
    value = TRUE
  )
last_change <- 
  as.character(
    format(max(file.info(source_files)$mtime), tz="UTC")
  )
```


```{r, results='asis', echo=FALSE}
cat(tmp$Version)
cat(" - ")
cat(stringb::text_replace(last_change, " ", " / "))
```

**Description**

```{r, results='asis', echo=FALSE}
cat(tmp$Description)
```


**License**

```{r, echo=FALSE}
cat(tmp$License, "\n\n")
cat(tmp$Author)
```




**Citation**

```{r, eval=FALSE}
citation("sar")
```

**BibTex for citing**

```{r, eval=FALSE}
toBibtex(citation("sar"))
```





## Installation


**Installation and start - development version**

```{r, eval=FALSE}
devtools::install_github("petermeissner/sar")
library(sar)
```



## Usage

```{r, eval=1}
library(sar)
```

```{r, include=FALSE}
sar_stat <- 
  function(...){
    tmp      <- sar::sar_stat(...)
    tmp$node <- "Server1"
    tmp
  }
```

**simple usage**

```{r}
sar_stat() %>% head()
```

**simple usage to wide format**

```{r}
sar_stat(to_wide = TRUE) %>% head()
```



**get data for yesterday**

```{r}
sar_stat(day = -1) %>% head()
```


**get data for day before yesterday**

```{r}
sar_stat(day = -2) %>% head()
```


**get data for last 20th calender day**

```{r}
sar_stat(day = 20) %>% head()
```

**get data for remote server**

```{r}
sar_stat(server = c("localhost", "localhost")) %>% head()
```


**and now vectorized on server and day**


```{r}
sar_stat(day = -c(1:5), server = c("localhost", "localhost")) %>% head()
```



**but best of all is plotting**

```{r}
# TBD #  sar_stat() %>% plot()
```
















